### 2017-02-08 pre_thesis/abstract.tex
Add latest version of thesis

\chapter{Introduction}

Further development in medical research require insight into complex
systems, that is too complicated to study with mathematical models and
super computers.

Further development in medical sciences cannot only rely on Moore's
law but also improvement on mathematical models and numerical
methods.

To lower the risk for the patient we need to more accuratley dioagnose
the patient, and find the optimal treatment.

Personalized medican at the level of the individual.

Many variables to take into account

The story of biomechanics starts in the 17th century with Giovanni
Borelli, known as the father of Biomechanics. He was the first one to
apply the mathematical techniques of Gallileo Galliei to study the
movement of animals.

\input{chapters/introduction/aim_of_thesis}
\input{chapters/introduction/physiology}
% \input{chapters/introduction/mechanics}
\input{chapters/introduction/patient}
\input{chapters/introduction/summary}

\pagebreak

\bibliographystyle{plain}
\bibliography{chapters/introduction/bibliography}

>>>>

\begin{abstract}
  Here is the abstract
\end{abstract}
